---
execute:
  echo: false
  warning: false
  message: false
format:
  docx:
    reference-doc: reach_tor_template.docx
    toc: false
    toc-depth: 3
    number-sections: true
---

```{r}
library(flextable)

tbl <- data.frame(
  text = c(
    "Research Terms of Reference",
    "[Research Cycle title]",
    "[Research Cycle ID]",
    "[Country]",
    "[Release date]",
    "[Version Number]"
  )
)

ft <- flextable(tbl)

ft <- delete_part(ft, part = "header")

# Page-width single column
ft <- width(ft, j = 1, width = 6.5)

# Font
ft <- font(ft, fontname = "Arial Narrow", part = "body")

# Text size
ft <- fontsize(ft, i = 1, size = 20, part = "body")
ft <- fontsize(ft, i = 2:4, size = 14, part = "body")
ft <- fontsize(ft, i = 5:6, size = 14, part = "body")

# Background colors
ft <- bg(ft, i = 1:4, j = 1, bg = "#EE5859", part = "body")
ft <- bg(ft, i = 5:6, j = 1, bg = "#58585A", part = "body")

# White text
ft <- color(ft, i = 1:6, j = 1, color = "white", part = "body")

# Alignment
ft <- align(ft, align = "left", part = "body")
ft <- valign(ft, valign = "center", part = "body")

# Line spacing
ft <- line_spacing(ft, space = 1, part = "body")

# Padding
ft <- padding(
  ft,
  padding.left = 12,
  padding.top = 1,
  padding.bottom = 1,
  part = "body"
)

# Optional emphasis
ft <- bold(ft, i = 1, bold = TRUE, part = "body")

# Remove all borders
ft <- border_remove(ft)

ft
```

\newpage

#### Assessment Summary

```{r}
library(flextable)

tbl <- data.frame(
  country = c("Country of intervention", "[Country]"),
  emergency = c("Type of Emergency", ""),
  crisis = c("Type of Crisis", ""),
  agency = c("Mandating Body/ Agency", "[Specify name(s) here]"),
  project_code = c("IMPACT Project Code", "[Eg. 99BSX]"),
  stringsAsFactors = FALSE
)

ft <- flextable(tbl)

ft <- delete_part(ft, part = "header")

# Page-width five-column table
ft <- width(ft, j = 1:5, width = 1.3)

# Font
ft <- font(ft, fontname = "Arial Narrow", part = "body")
ft <- fontsize(ft, size = 9, part = "body")

# Header row formatting
ft <- bold(ft, i = 1, bold = TRUE, part = "body")
ft <- bg(ft, i = 1, bg = "#DDDDDE", part = "body")
# Alignment
ft <- align(ft, align = "left", part = "body")
ft <- valign(ft, valign = "top", part = "body")

# Padding and spacing
ft <- padding(ft, padding = 4, part = "body")
ft <- line_spacing(ft, space = 0.9, part = "body")

# Borders
ft <- border_outer(ft, part = "all")
ft <- border_inner_h(ft, part = "body")
ft <- border_inner_v(ft, part = "body")

ft
```


```{r}
library(flextable)

tbl <- data.frame(
  geographic_coverage = c("Geographic Coverage", "[Specify geographic coverage]"),
  population = c("Population(s)", "[Specify population(s)]"),
  stratification = c("Stratification", "[Specify stratification]"),
  stringsAsFactors = FALSE
)

ft <- flextable(tbl)

ft <- delete_part(ft, part = "header")

# Page-width three-column table
ft <- width(ft, j = 1:3, width = 2.17)

# Font
ft <- font(ft, fontname = "Arial Narrow", part = "body")
ft <- fontsize(ft, size = 9, part = "body")

# Header row formatting
ft <- bold(ft, i = 1, bold = TRUE, part = "body")
ft <- bg(ft, i = 1, bg = "#DDDDDE", part = "body")

# Alignment
ft <- align(ft, align = "left", part = "body")
ft <- valign(ft, valign = "top", part = "body")

# Padding and spacing
ft <- padding(ft, padding = 4, part = "body")
ft <- line_spacing(ft, space = 0.9, part = "body")

# Borders
ft <- border_outer(ft, part = "all")
ft <- border_inner_h(ft, part = "body")
ft <- border_inner_v(ft, part = "body")

ft
```

#### Tools and Methods

```{r}
library(flextable)

tbl <- data.frame(
  tool = c(
    "Tool",
    "Household Tool",
    "Community KII",
    "Community Observation",
    "Health Facility KII",
    "Health Facility Observation",
    "Nutrition Facility KII",
    "FSL Provider KII",
    "Market KII",
    "Crops/Livestock Observation",
    "WASH Provider KII",
    "Water Point Observation",
    "Latrine Observation"
  ),
  dimensions = c("Dimensions", rep("", 12)),
  sampling_method = c("Sampling Method", rep("", 12)),
  sample_size = c("Sample Size", rep("", 12)),
  stringsAsFactors = FALSE
)

ft <- flextable(tbl)

ft <- delete_part(ft, part = "header")

# Page-width five-column table
ft <- width(ft, j = 1:4, width = 1.3)

# Font
ft <- font(ft, fontname = "Arial Narrow", part = "body")
ft <- fontsize(ft, size = 9, part = "body")

# Header row formatting
ft <- bold(ft, i = 1, bold = TRUE, part = "body")
ft <- bg(ft, i = 1, bg = "#DDDDDE", part = "body")

# Alignment
ft <- align(ft, align = "left", part = "body")
ft <- valign(ft, valign = "top", part = "body")

# Padding and spacing
ft <- padding(ft, padding = 4, part = "body")
ft <- line_spacing(ft, space = 0.9, part = "body")

# Borders
ft <- border_outer(ft, part = "all")
ft <- border_inner_h(ft, part = "body")
ft <- border_inner_v(ft, part = "body")

ft
```

#### Research Timeline

```{r}
#| echo: false
#| warning: false
#| message: false
#| fig-width: 7
#| fig-height: 2

library(ggplot2)

timeline_df <- data.frame(
  date = as.Date(c(
    "2027-01-15",
    "2027-02-01",
    "2027-03-15",
    "2027-04-01",
    "2027-04-15",
    "2027-05-01",
    "2027-05-15",
    "2027-06-01",
    "2027-06-15"
  )),
  milestone = c(
    "1. Pilot / training",
    "2. Start collect data",
    "3. Data collected",
    "4. Data analysed",
    "5. Data sent for validation",
    "6. Preliminary presentation",
    "7. Outputs sent for validation",
    "8. Outputs published",
    "9. Final presentation"
  ),
  y_line_end = c(
    0.125, -0.125,
  0.125, -0.125,
  0.125, -0.125,
  0.125, -0.125,
  0.125
  ),
  y_text = c(
    0.18, -0.18,
  0.18, -0.18,
  0.18, -0.18,
  0.18, -0.18,
  0.18
  ),
  stringsAsFactors = FALSE
)

timeline_df$label <- paste0(
  timeline_df$milestone,
  "\n",
  format(timeline_df$date, "%d %b %Y")
)

timeline_plot <- ggplot(timeline_df, aes(x = date, y = 0)) +
  geom_line(
    colour = "#58585A",
    linewidth = 0.8
  ) +
  geom_point(
    colour = "#EE5859",
    size = 3
  ) +
  geom_segment(
    aes(
      x = date,
      xend = date,
      y = 0,
      yend = y_line_end
    ),
    colour = "#58585A",
    linewidth = 0.4
  ) +
  geom_text(
  data = subset(timeline_df, y_text > 0),
  aes(
    x = date,
    y = y_text,
    label = label
  ),
  angle = 30,
  hjust = 0,
  vjust = 0.5,
  family = "Arial Narrow",
  size = 2.8,
  lineheight = 0.9
) +
geom_text(
  data = subset(timeline_df, y_text < 0),
  aes(
    x = date,
    y = y_text,
    label = label
  ),
  angle = -30,
  hjust = 0,
  vjust = 0.5,
  family = "Arial Narrow",
  size = 2.8,
  lineheight = 0.9
) +
  scale_x_date(
    date_breaks = "1 month",
    date_labels = "%b\n%Y"
  ) +
  coord_cartesian(
    ylim = c(-0.7, 0.8),
    clip = "off"
  ) +
  theme_minimal() +
  theme(
    text = element_text(family = "Arial Narrow"),
    axis.title = element_blank(),
    axis.text.y = element_blank(),
    axis.ticks.y = element_blank(),
    axis.text.x = element_blank(),
    axis.ticks.x = element_blank(),
    panel.grid.major.y = element_blank(),
    panel.grid.minor = element_blank(),
    panel.grid.major.x = element_blank(),
    plot.margin = margin(
      t = 25,
      r = 30,
      b = 25,
      l = 20
    )
  )

timeline_plot
```

#### Dissemination

```{r}
library(flextable)

tbl <- data.frame(
  audience_type = c(
    "Audience Type",
    "Cluster(s)",
    "Donor(s)",
    "Operational Actor(s)",
    "Other(s)"
  ),
  expected_output_type = c(
    "Expected Output Type",
    rep("", 4)
  ),
  dissemination_strategy = c(
    "Dissemination Strategy",
    rep("", 4)
  ),
  access = c(
    "Access",
    rep("", 4)
  ),
  visibility = c(
    "Visibility",
    rep("", 4)
  ),
  stringsAsFactors = FALSE
)

ft <- flextable(tbl)

ft <- delete_part(ft, part = "header")

# Page-width five-column table
ft <- width(ft, j = 1:5, width = 1.3)

# Font
ft <- font(ft, fontname = "Arial Narrow", part = "body")
ft <- fontsize(ft, size = 9, part = "body")

# Header row formatting
ft <- bold(ft, i = 1, bold = TRUE, part = "body")
ft <- bg(ft, i = 1, bg = "#DDDDDE", part = "body")

# Alignment
ft <- align(ft, align = "left", part = "body")
ft <- valign(ft, valign = "top", part = "body")

# Padding and spacing
ft <- padding(ft, padding = 4, part = "body")
ft <- line_spacing(ft, space = 0.9, part = "body")

# Borders
ft <- border_outer(ft, part = "all")
ft <- border_inner_h(ft, part = "body")
ft <- border_inner_v(ft, part = "body")

ft
```

\newpage

# Executive Summary

# Rationale

## Background

## Intended Impact

\newpage

# Goals and Objectives

## Overall Goal and Research Questions

## Specific Goals and Research Questions

\newpage

# Methodology

#### Methodology Overview

#### Population of Interest

#### Secondary Data Review

#### Key Definitions

#### Primary Data Collection

##### Household Surveys

###### Sample Size Calculations

###### Site Selection Methods

###### Household Selection Methods

##### Key Informant Interviews

###### Key Informant Interview Overview

###### Key Informant Selection

##### Observation Tools

###### Observation Tools Overview

#### Data Processing and Analysis

###### Household Survey Data

###### Key Informant and Observation Data

#### Integrated Analysis

#### Limitations

\newpage

# Key Ethical Considerations and Related Risks

# Roles and Responsibilities

\newpage

# Data Analysis Plan (DAP)

#### Household Tool DAP

#### Community Key Informant DAP

#### Community Observation DAP

#### Health Facility KII DAP

#### Health Facility Observation DAP

#### Nutrition Facility DAP

#### FSL Provider KII DAP

#### Market KII DAP

#### WASH Provider KII DAP

#### Water Point Observation DAP

#### Latrine Observation DAP

